### 2015-03-28 Kokkos_PG_MachineModel.tex
Adds Hennessy and Paterson reference and a section for atomic memory references.

>>>>

\subsubsection{Memory Consistency in Kokkos}

Memory consistency models are a complex topic in and of themselves
and usually rely on complex operations associated with hardware
caches (for more information see reference~\cite{handp_hardware}. 
Kokkos itself does not {\em require} caches to be present
in hardware and so assumes an extremely weak memory consistency
model. In this model, the programmer should not assume any
specific ordering of memory operations being isused by a
kernel. This has the potential to create race conditions between
memory operations if these are not appropriately protected. In
order to provide a guaranteed that memory are completed, Kokkos
provides a {\em fence} operation which forces the compute 
engine to complete all outstanding memory operations before
any new ones can be issued. With appropriate use of fences,
programmers are thereby able to ensure that guarantees can
be made as to when data will {\em definitely} have been 
written to memory.

\subsubsection{Atomic accesses to Memory in Kokkos}
